\huge{\textbf{Gesture Based UI Development}} \\ \LARGE{Research Paper}

### 2021-02-13 paper/main.tex
Subsection 'The Touch Screen' complete.

%%% CONTENT START HERE %%%%
\section{Description}
This Research Paper is based on Gesture Based User Interface Experience that focuses on Accessibility, Evolution, and Challenges. The purpose of this paper is to research the User Interface as it moves from purely physical (mouse, keyboard, touch screen) to include intuitive interaction through gestures.

@@

\section{User Experience Evolution}
\subsection{Early Days of User Experience}
User Experience is constantly Evolving. The first general-purpose computer was the monolithic ENIAC machine. The machine's construction began on the 13th of May, 1943, and was finished on the 2nd of October, 1955. The User Experience on the ENIAC was a bit of a headache and relied on many experts to work the machine. ENIAC was designed to be capable of being reprogrammed to solve a large number of numerical problems. The machine's programming consisted of setting switches and connecting wires according to specific instructions, which were first worked out on paper, which took weeks. This machine also used a punch-card reader as an input and output device. This is obviously not very user-friendly, but for the time, it was extraordinary. Comparing this machine to any computer or smart device today shows how much these technologies have evolved.
\cite{ref1}

@@

In the 1980s, computer screens became revolutionary with the use of CGA (Color Graphics Adapter) and EGA (Enhanced Graphics Adapter) that were both introduced by IBM. These brought colour and higher resolution to computer screens. Followed by these displays, the Macintosh Monitors came, and they used bitmapped graphics. The Mac II's (1978) video standard was quite similar to the VGA (Video Graphics Array). Mac monitors continued to evolve and were always known for their sharpness and accurate color representation.

@@

\newpage
\subsection{The Touch Screen}

@@

\subsection{Virtual and Augmented Spaces}

@@

\section{Gestures as a Communication Tool}

\section{Challenges for the Design of Applications}

\section{Challenges for Implementation}

\section{Conclusions}

@@

\bibitem{ref2} SUZANNE DEFFREE - EDN - Construction begins on ENIAC
\newline
URL: \url{https://www.edn.com/construction-begins-on-eniac-may-31-1943/}

@@

>>>>

%%% START OF CONTENT %%%%
\section{Description}
This Research Paper is based on Gesture Based User Interface Experience that focuses on Accessibility, Evolution, and Challenges. The purpose of this paper is to research the User Interface as it moves from purely physical (mouse, keyboard, touch screen) to include intuitive interaction through gestures.

@@

\section{User Experience Evolution}
% Originally with just a keyboard and screen, computers have evolved to include
% a mouse, touch screen, voice control, virtual augmented spaces and gesture
% recognition. What is the User Experience and what are the drivers in the
% evolution process? Why are user’s never happy with the current iteration of
% interaction with computing systems? What are the challenges faced by each
% generation as new interactions are marketed to users from both acceptance and
% implementation perspectives?

\subsection{Early Days of User Experience}
User Experience is constantly Evolving. The first general-purpose computer was the monolithic ENIAC machine. The machine's construction began on the 13th of May, 1943, and was finished on the 2nd of October, 1955. The User Experience on the ENIAC was a bit of a headache and relied on many experts to work the machine. ENIAC was designed to be capable of being reprogrammed to solve a large number of numerical problems. The machine's programming consisted of setting switches and connecting wires according to specific instructions, which were first worked out on paper, which took weeks. This machine also used a punch-card reader as an input and output device. This is obviously not very user-friendly, but for the time, it was extraordinary. Comparing this machine to any computer or smart device today shows how much these technologies have evolved.
\cite{ref1}

@@

In the 1980s, computer screens became revolutionary with the use of CGA (Colour Graphics Adapter) and EGA (Enhanced Graphics Adapter) that were both introduced by IBM. These brought colour and higher resolution to computer screens. Followed by these displays, the Macintosh Monitors came, and they used bitmapped graphics. The Mac II's (1978) video standard was quite similar to the VGA (Video Graphics Array). Mac monitors continued to evolve and were always known for their sharpness and accurate colour representation.

@@

\newpage
\subsection{The Touch Screen}
Touch Screen technology has become vastly popular throughout the years. Touchscreens are everywhere. They can be on PCs, laptops, smartphones, smartwatches, cameras, and almost every other electronic device with a screen. The touchscreen originated in the 1960s. E.A. Johnson invented the first finger-driven touchscreen in 1965. This touchscreen mechanism is used in many smartphones today—what now is know as capacitive touch. An insulator, like glass, coated with a transparent conductor (such as Indium Tin Oxide) is used by the capacitive touchscreen panel. Usually, the 'conductive' part is a human finger or a touch pen. Johnson's initial touchscreen could only process one touch at a time, and what is describe today as 'multi-touch' was still years away. By 1971, a number of different machines with touchscreens were introduced. One of these machines was the Plato IV, which was the first touchscreen computer to be used in a classroom. This allowed students to touch the screen to select answers to questions. The PLATO IV employed infrared technology rather than capacitive or resistive. 
\cite{ref8}

\begin{figure}[!ht]
    \caption{The PLATO IV touchscreen terminal}
    \label{image:PLATOIV}
    \centering
    \includegraphics[width=0.5\textwidth]{pics/plato_iv.jpg}
\end{figure}

At the beginning of the 1980s, touchscreens began heavily commercialized. HP created a computer called the HP-150 in 1983. The HP-150 used MS-DOS and featured a 9inch Sony CRT surrounded by infrared (IR) emitters and detectors that sensed where the user's finger came down the screen. The HP-150 was not immediately embraced because it had usability issues. For example, poking at the screen would, in turn, block other IR rays that could tell the computer where the user's finger was pointing.

IBM and BellSouth teamed up in 1993 to launch the Simon Personal Communicator (SPC). The SPC was one of the first cellphones that possessed a touchscreen. The phone featured paging capabilities, an e-mail and calendar application, an appointment schedule, an address book, a calculator, and a pen-based sketchpad. The touchscreen was resistive, which required a stylus to navigate through menus and to input data.
\cite{ref8}

\begin{figure}[!ht]
    \caption{IBM's Simon Personal Communicator}
    \label{image:SPC}
    \centering
    \includegraphics[width=0.4\textwidth]{pics/IBM_Simon.jpeg}
\end{figure}

In the 2000s, touchscreen technology flourished. There were advancements during this time that helped bring multi-touch and gesture-based technology to the masses. The 2000s were also the era when touchscreens became the favorite tool for design collaboration. The first human-controlled multi-touch device was invented at the University of Toronto in 1982 by Nimish Mehta. It featured a frosted glass panel in front of a camera, which detected action when it identified ‘black spots’ showing up onscreen.
As the 2000s approached, companies poured more resources into integrating touchscreen technology into their daily processes. With the arrival of the PortfolioWall 3D animators and designers were primarily targeted. PortfolioWall was a large-format touchscreen meant to be a dynamic version of the boards that design studios use to track projects.  The PortfolioWall had a gesture-based interface that was simple and easy-to-use. It allowed users to inspect and maneuver images, animations, and 3D files. 
\cite{ref8}

\begin{figure}[!ht]
    \caption{PortfolioWall}
    \label{image:PFW}
    \centering
    \includegraphics[width=0.5\textwidth]{pics/pf_wall.jpg}
\end{figure}

Sony unveiled a flat input surface named SmartSkin in 2002 that could simultaneously identify multiple hand configurations and touch-points by measuring the distance between the hand and the surface using capacitive sensing and a mesh-shaped antenna.
The project's ultimate aim was to turn surfaces seen every day, such as an ordinary table or a wall, into an immersive one using a nearby PC.

In 2007 Microsoft introduced the Surface at the All Things D conference. Although many of its design concepts were not new, it very effectively illustrated the real-world use case for touchscreens embedded into something the size of a coffee table. Microsoft designed the Surface to be used by their commercial customers to give users a sample of the hardware. Firms such as AT\&T used the Surface to display the latest handsets to buyers visiting their brick and mortar retail locations.

These technologies cannot be understated, as each had a monumental impact on the electronic devices we use today. Everything from PCs, laptops, smartphones, smartwatches, cameras can connect to the numerous innovations, discoveries, and patents in the history of touchscreen technology.
\cite{ref8}

@@

\newpage
\subsection{Virtual and Augmented Spaces}

@@

\section{Gestures as a Communication Tool}
% How are gestures used in everyday life for communication with others? They
% are a universal tool albeit without a unilateral meaning and interpretation.
% How are gestures defined and become accepted to represent various aspects of
% communication?

\subsection{How are gestures used in everyday life for communication with others?}
\subsection{How are gestures defined and become accepted to represent various aspects of
communication?}

\section{Challenges for the Design of Applications}
% Incorporating gestures is an important part of the design phase. Using the
% wrong gestures will leave users confused and frustrated as they learn a new
% system. The functionality of the system has to be appropriately mapped to
% the gesture set available in such a way to reduce the learning curve and the
% resistance gradient of the user

\section{Challenges for Implementation}
% Deciding that a particular gesture should carry out a particular function is one
% thing, actually tracking that gesture and deciding when it has been made is a
% different challenge. Looking at some systems and the gestures they use, what
% are the challenges in implementation that had to be overcome for those systems?
% How were those challenges met (if they were met)?

\section{Conclusions}
% Conclusions are what you have learned from your research. This is your reflection on the current state of the art and the possible future directions of gesture-based user interfaces.

%%% END OF CONTENT %%%%

@@

\bibitem{ref2} Suzanne Deffre - EDN - Construction begins on ENIAC
\newline
URL: \url{https://www.edn.com/construction-begins-on-eniac-may-31-1943/}

@@

\bibitem{ref8} Florence Ion - From touch displays to the Surface
\newline
URL: \url{https://tinyurl.com/ycpwsg8m}
